---
title: "Analysis Workflow"
author: "Connor Elfers"
date: "4/5/2022"
output: html_document
---

## Do before using functions

Load libraries needed.

```{r setup, include=FALSE}
library(textdata)
library(XML)
library(tm)
library(tidytext)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(reshape2)
library(readxl)
library(twitteR)
library(plotly)
library(scales)
library(GGally)
library(shiny)

#install data set to use
twitter.data <- read_xlsx("C:/Users/Connor Elfers/Documents/USF Classes/Spring 2022/LIS 4370 (R Programming)/Triangulation Project/Package/ElfTri Package/ElfTri/data/Squid Game Twitter data 1.xlsx")
head(twitter.data)



```


## Function 1: clean()


The purpose of this function is to clean the data set of arbitrary columns, data entries with NA's within, and removes some of the largest outliers from the three major categories this analysis focuses on.  Uses the provided data set as the argument. Use first before all other functions.



```{r, clean}

clean <- function(x) {
  twitter.data <- x

  name <- "Twitter_Activity"
  colnames(twitter.data)[3] <- name
  head(twitter.data)
  twitter.data <- twitter.data[,-8:-11]
  twitter.data <- na.omit(twitter.data)

  twitter.data[which.max(twitter.data$Engagement),] # major outlier skewed graph
  match("bigbertha12", twitter.data$Username)
  twitter.data <- twitter.data[-160,]
  rownames(twitter.data) <- NULL


  # Tidy up Min and Max for graph : Retweets
  twitter.data[which.max(twitter.data$Twitter_Activity),] # another major outlier
  match("danaiguriratwd", twitter.data$Username)
  twitter.data <- twitter.data[-704,]
  rownames(twitter.data) <- NULL


  # Tidy up Min and Max for graph : Impressions
  twitter.data[which.max(twitter.data$Impressions),]
  match("naaaaaaateb", twitter.data$Username)
  twitter.data <- twitter.data[-644,]
  rownames(twitter.data) <- NULL

  return(twitter.data)

}

twitter.data <- clean(twitter.data)

```





## Function 2: graph.token()

The purpose of this function is to take the data from the Comments column, tokenize the terms, clean by removing common and custom stop words, arrange in descending order, and graphing the top 15 most frequently mentioned terms. Uses a data frame as an arugment.


```{r, graph.token}


# Creates plot of top 15 most frequent terms

graph.token <- function(x) {
  custom.stop.words <- tribble(
    ~word, ~lexicon,
    "http", "CUSTOM", # Common URL term
    "twd", "CUSTOM", # Within top 15, I don't know what twd means, Better to leave it out I suppose.
    "t.co", "CUSTOM", # IDK what this term is but it's a common one regarding twitter data that is not useful.
    "de", "CUSTOM", # Also in top 15, I don't think it's useful.
    "13", "CUSTOM",
    "16", "CUSTOM",
    "im", "CUSTOM" # Not needed
  )

  # Bind custom to original
  new.stop.words <- stop_words %>% bind_rows(custom.stop.words)
  # Apply new stop words
  y <- x %>% unnest_tokens(word, Comments) %>% anti_join(new.stop.words)

  # ggplot graph 15 most common
  z <- y %>% count(word) %>% arrange(desc(n))%>% top_n(15) %>% mutate(word = reorder(word, n)) %>% ggplot(aes(x = word, y = n)) +
    geom_col(aes(fill = word)) + labs( y = "Frequency", x = "Terms", title = "Top 15 Most Frequent Terms") + coord_flip() +
    theme(legend.position = "none")

  return(z)
}


graph.token(twitter.data)

```

## Function 3: graph.sentiment()

This function is very similar to previous function the main difference is that we add a layer of sentiment analysis to it. Instead of graphing top 15 frequent terms this function produces a graph of the top 10 most frequent terms grouped by negative and positive sentiment. Uses data frame variable for argument.

```{r, graph.sentiment}

graph.sentiment <- function(x) {
  custom.stop.words <- tribble(
    ~word, ~lexicon,
    "http", "CUSTOM", # Common URL term
    "twd", "CUSTOM", # Within top 15, I don't know what twd means, Better to leave it out I suppose.
    "t.co", "CUSTOM", # IDK what this term is but it's a common one regarding twitter data that is not useful.
    "de", "CUSTOM", # Also in top 15, I don't think it's useful.
    "13", "CUSTOM",
    "16", "CUSTOM" # Not needed
  )

  # Bind custom to original
  new.stop.words <- stop_words %>% bind_rows(custom.stop.words)
  # Apply new stop words
  y <- x %>% unnest_tokens(word, Comments) %>% anti_join(new.stop.words)


  z <- y %>% inner_join(get_sentiments("nrc")) %>%
    filter(sentiment %in% c("positive", "negative")) %>% count(word, sentiment) %>%
    group_by(sentiment) %>% top_n(10, n) %>% ungroup() %>% mutate(
      word2 = fct_reorder(word, n))

  graph <- ggplot(z, aes(x = word2, y = n, fill = sentiment)) +
    geom_col(show.legend = FALSE) +facet_wrap(~sentiment, scale = "free") +
    coord_flip() + labs(y = "Frequency", x = "Terms")

  return(graph)
}


graph.sentiment(twitter.data)

```

## Function 4: graph.trio()

The purpose of this function is that it produces three different graphs based off of Pierce's Sign theory of triangulation. These graphs focuses on the variables Engagement, Twitter_Activity, and Impressions to see how they interact with one another. It produces a bubble graph, bar graph of total sum of all three, and a line graph. Each graph has been modified to show the most relevant data by 'zooming' in on the high concentrated areas. Uses the imported data frame as an argument.


```{r, graph.trio}

graph.trio <- function(x) {

  data <- x

  Bubble <- ggplot(data, aes(x = Twitter_Activity, y = Engagement)) +
    geom_point(aes(size = Impressions), alpha = 0.3, color = "blue") +
    xlim(0, 1000) + ylim(100, 1000)  + scale_size(range = c(2, 10), limits = c(0,25000)) +
    labs(title = "Squid Game through Peirce's sign theory")



  focus <- x[, c(3:5)]

  retweetSum <- colSums(focus[,1])
  retweetSum

  ImpresSums <- colSums(focus[,2])
  ImpresSums

  EngagSum <- colSums(focus[,3])
  EngagSum

  allSums <- c(retweetSum, ImpresSums, EngagSum)
  names <- c("Twitter_Activity", "Impressions", "Engagement")

  barDF <- data.frame(allSums, names)

  Bar <- ggplot(barDF, aes(x = names, y = allSums, fill = names)) + geom_col() +
    labs(x = "Variable Types", y = "Total Sums", title = "Squid Game through Peirce's sign theory") +
    scale_y_continuous(limits=c(0,3000000), oob = rescale_none, labels = comma) + theme(legend.position = "none")


  line <- ggplot(x, aes(x = Impressions, y = Engagement, color = Twitter_Activity)) + geom_line(size = 1) +
    labs(title = "Squid Game through Peirce's sign theory") + scale_color_continuous(high = "black", low = "orange") +
    scale_x_continuous(limits = c(0, 3000)) + scale_color_continuous(high = "black", low = "orange", limits = c(0, 1000))

  z <- list(Bubble, Bar, line)

  return(z)

}


graph.trio(twitter.data)

```


## Function 5: shinySG()


The purpose of this function creates a simple interactive graph that allows for real time changing of values on a scatter plot. You are able to choose between the x and y axis and the color of the data points. Uses the imported data frame as an argument. 


```{r, shinySG}

shinySG <- function(x) {
  ui <- fluidPage(
    sidebarLayout(
      sidebarPanel(
        # Use pop size for x and y axis
        selectInput("variableX", "X-Axis:",
                    c("Likes" = "Impressions",
                      "Retweets" = "Twitter_Activity",
                      "Engagement" = "Engagement"
                    )),


        selectInput("variableY", "Y-Axis:",
                    c("Engagement" = "Engagement",
                      "Likes" = "Impressions",
                      "Retweets" = "Twitter_Activity"

                    )),


        selectInput("variableC", "Color:",
                    c( "Retweets" = "Twitter_Activity",
                       "Likes" = "Impressions",
                       "Engagement" = "Engagement"
                    )),

      ),

      mainPanel(plotOutput(outputId = "plot"))
    )
  )


  server <- function(input, output) {

    data <- data.frame(x)

    output$plot <- renderPlot({ggplot(data, aes(x = data[, input$variableX], y = data[, input$variableY], fill = data[, input$variableC])) +
        geom_point(size = 3, pch = 21) + scale_x_continuous(limits = c(0, 10000)) + scale_y_continuous(limits = c(0, 10000)) + scale_fill_continuous(limits = c(0, 5000), high = "orange", low = "white") +
        labs(Title = "Squid Game through Peirce's sign theory", x = input$variableX, y = input$variableY, size = input$variableS, fill = input$variableC)
    }, height = 600, width = 750)


  }

  shine <- shinyApp(ui = ui, server = server)
  return(shine)

}

shinySG(twitter.data)

```
